---
title: "Study 3 Initial Graphs"
output: pdf_document
date: "2024-11-22"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

pilot_long<-read.csv("study_3_long_clean.csv")
pilot<-read.csv("study_3_clean.csv")

#we're gonna start w/ gtsummary, since that's how we closed it out originally
library("lme4")
library("texreg")
library("ggplot2")
library("tidyverse")
library("gtable")
library("gtsummary")
library("reshape2")
library(data.table)
pilot_xtra_long<-melt(setDT(pilot_long),measure=patterns("_familiar", "_change", "_support", "_mconv"), 
                      value.name=c("topic_familiarity", "topic_changeable", "topic_support", "topic_moral_c"),
                      variable.name="topic")
#subset out the 'pre' results so we can see baseline differences

#rename the topics lol

pilot_xtra_long$topic<-str_replace_all(pilot_xtra_long$topic, c("1"= "uhc", "2" = "cap", "3" = "ai"))

pilot_xtra_long<-subset(pilot_xtra_long,time == 'Pre')
```

## Initial Report

We see some initial differences in topic familiarity; similar but less so differences in topic 'changeablity'. A significant difference in baseline support for UHC, as well ase for baseline moral conviction


```{r 1graphs}
plot1a<-ggplot(pilot_xtra_long, aes(x=topic, y=topic_familiarity, color=topic)) +
  geom_boxplot() +labs(
  )
plot1a + scale_color_brewer(palette = "Set1")

plot1b<-ggplot(pilot_xtra_long, aes(x=topic, y=topic_changeable, color=topic)) +
  geom_boxplot() +labs(
  )
plot1b + scale_color_brewer(palette = "Set1")

plot1c<-ggplot(pilot_xtra_long, aes(x=topic, y=topic_support, color=topic)) +
  geom_boxplot() +labs(
  )
plot1c + scale_color_brewer(palette = "Set1")
#a priori support is nice and high for uhc, but p strongly against the other two!

plot1d<-ggplot(pilot_xtra_long, aes(x=topic, y=topic_moral_c, color=topic)) +
  geom_boxplot() +labs(
  )
plot1d + scale_color_brewer(palette = "Set1")
```

### Effects on UHC
No effects on moral conviction; pre-post differences for support, however, no differences between interventions.

```{r 2graphs}
#subset of post results only?
plot2a<-ggplot(pilot_long, aes(x=consen_cond, y=uhc_support, color=conv_cond)) +
  geom_boxplot() +labs(
  )+facet_wrap(vars(time))

#added the wrapper
plot2a + scale_color_brewer(palette = "Set1")

#consensus seems to impact, but NOT conviction? for at least general support

plot2b<-ggplot(pilot_long, aes(x=consen_cond, y=uhc_mconv, color=conv_cond)) +
  geom_boxplot() +labs(
  )+facet_wrap(vars(time))

plot2b + scale_color_brewer(palette = "Set1")

```


### Effects on Capital Punishment
Main effect of social consensus condition, such that being in the 'low' block resulted in lower moral conviction, with an interaction between social consensus and moral conviction, such that participants who have been in the pragmatic condition, reverses the effect of being in the low social consensus condition;Again, pre-post differences for support, however, no differences between interventions.

```{r 3graphs}
plot3a<-ggplot(pilot_long, aes(x=consen_cond, y=cap_support, color=conv_cond)) +
  geom_boxplot() +labs(
  )+facet_wrap(vars(time))

plot3a + scale_color_brewer(palette = "Set1")

#consensus seems to impact, but NOT conviction? for at least general support

plot3b<-ggplot(pilot_long, aes(x=consen_cond, y=cap_mconv, color=conv_cond)) +
  geom_boxplot() +labs(
  )+facet_wrap(vars(time))

plot3b + scale_color_brewer(palette = "Set1")

```

### Effects on AI in the workplace
No effects on moral conviction; Again, pre-post differences for support, however, no differences between interventions.


```{r 4graphs}
plot4a<-ggplot(pilot_long, aes(x=consen_cond, y=ai_support, color=conv_cond)) +
  geom_boxplot() +labs(
  )+facet_wrap(vars(time))

plot4a + scale_color_brewer(palette = "Set1")
#consensus seems to impact, but NOT conviction? for at least general support

plot4b<-ggplot(pilot_long, aes(x=consen_cond, y=ai_mconv, color=conv_cond)) +
  geom_boxplot() +labs(
  )+facet_wrap(vars(time))

plot4b + scale_color_brewer(palette = "Set1")
```

### Some extra graphs

```{r 5graphs}
plot6a<-ggplot(pilot, aes(x=in_ai_change, y=fn_ai_supp, color=consen_cond)) +
  geom_point() +labs(
  ) + geom_smooth( method = "lm")

plot6a + scale_color_brewer(palette = "Set1")


#scatterplot for final capital punishment support as affected by openness to cap change#

plot6b<-ggplot(pilot, aes(x=in_cap_change, y=fn_cap_supp, color=consen_cond)) +
  geom_point() +labs(
  ) + geom_smooth( method = "lm")

plot6b + scale_color_brewer(palette = "Set1")
```